\documentclass[12pt, a4paper, margin=0.8in]{article}
\usepackage{scimisc-cv}
\usepackage{setspace}
\usepackage{multicol}
\usepackage{hyperref}

\title{Curriculum Vitae}
\author{Thirumala Devi Sanaboyina}
\date{\today}

\cvname{THIRUMALA DEVI SANABOYINA}
\cvpersonalinfo{
Hyderabad, India \cvinfosep
thirumaladevisanaboyina@gmail.com \cvinfosep
\href{https://www.linkedin.com/in/thirumala-devi}{LinkedIn} | \href{https://github.com/thirumala-devi}{GitHub} \cvinfosep
+91 9898899724
}

\begin{document}

\makecvtitle

\setstretch{1.23}

\section*{Summary}
Skilled in developing dynamic, data-driven websites using Django and Python, with expertise in designing responsive and visually appealing user interfaces through HTML and Bootstrap. Strong experience in implementing secure, scalable applications, optimizing performance, and ensuring seamless user experiences across various devices and platforms.

\section{Education}

\cvsubsection{JNTUK - Swarnandhra Institute of Engineering and Technology}
[Andhra Pradesh, India]
{\textbf{Bachelor of Technology in Computer Science Engineering} \hfill 2023}

\cvsubsection{GTU - Tolani Foundation Gandhidham Polytechnic}
[Gujarat, India]
{\textbf{Diploma in Computer Science Engineering} \hfill 2020}

\cvsubsection{Atmiya Vidhya Peeth}
[Gujarat, India]
{\textbf{CBSE} \hfill 2016}

\section{Professional Experience}

\cvsubsection{Datapoint IT \& Hardware Tech Private Limited}
[Hyderabad, India] [\textbf{Software Engineer (Django Developer)}] [2025 - Present]
\begin{itemize}
    \item Conducted Python and Django training sessions, sharing knowledge and expertise with team members.
    \item Developed Python projects integrated with the Django framework, ensuring robust and scalable solutions.
\end{itemize}

\cvsubsection{Ramanasoft IT Consultancy Services}
[Hyderabad, India] [\textbf{Web Developer Intern}] [2024]
\begin{itemize}
    \item Developed an e-commerce food application during my internship at Ramana Soft.
    \item Implemented and integrated admin and user panels.
    \item Managed data insertion and performed data analysis operations.
    \item Collaborated with team on optimizing application performance and functionality.
    \item Successfully deployed the fully operational project.
\end{itemize}

\section{Projects}

\cvsubsection{Virtual Mouse Operation Using Webcam}
\begin{itemize}
    \item Designed a cost-free hand recognition system for controlling laptops and PCs using an IoT device (webcam).
    \item Developed an alternative to traditional mouse systems for enhanced accessibility.
\end{itemize}



\section{Certifications}
\begin{itemize}
    \item \textbf{Full stack python certification}, IHub, 2024
    \item \textbf{ certification}, IHub, 2024
\end{itemize}

\section{Technical Skills}
\begin{multicols}{2}
\begin{minipage}{0.6\textwidth}
    \begin{itemize}
        \item \textbf{Languages:} Python, JavaScript
        \item \textbf{Frameworks:} Django, Bootstrap
    \end{itemize}
\end{minipage}%
\hfill%
\begin{minipage}{0.4\textwidth}
    \begin{itemize}
        \item \textbf{Frontend:} HTML, CSS
        \item \textbf{Databases:} MySQL
    \end{itemize}
\end{minipage}
\end{multicols}




\end{document}
